\subheading{Examples and unit tests}

Examples and unit tests both execute CORA functionality.
Their main difference is the audience:
\begin{itemize}
	\item Examples (\verb|cora/examples|) are geared towards \emph{users}:
		They should \emph{show} the functionality of the code.
		Ideally, a plot illustrates the result.
		Only the most important functions require examples.
		Examples can comprise more functions at the same time.
	\item Unit tests (\verb|cora/unitTests|) are geared towards \emph{developers}:
		They should \emph{check} the functionality of the code.
		Their output argument is \verb|true| or \verb|false| corresponding to a successful or flawed execution of the test.
		Each unit test check only a single function (omitting dependencies within the function itself).
\end{itemize}

There are different types of unit tests:
\begin{itemize}
	\item Analytical:
		These tests compare the result of a function to an analytical solution.
		All test cases should be deterministic.
		They are the strongest types of unit tests.
	\item Random tests:
		These tests use randomly generated cases to check a wide variety of different evaluations.
		The result can be checked to be within an acceptable range.
		They are useful to find bugs which occur in edge cases.
	\item Saved result:
		These tests compare the result of a function to a previously saved result which is known to be correct.
	\item Execution tests:
		These tests merely prove if the function ran through.
		The result is not checked numerically.
\end{itemize}

Furthermore, there are different unit test suites:
\begin{itemize}
	\item \verb|runTestSuite|:
		This test suite calls all functions with the prefix \verb|test_|.
		These tests should be quickly executable (about 5min in total) so that one can quickly detect error in the installation of CORA or undesired but far-reaching bugs.
		Moreover, there should be no random tests.
	\item \verb|runTestSuite_longDuration|:
		This test suite calls all functions with the prefix \verb|testLongDuration_|.
		These tests should be much more thorough than the standard test suite, as they are mostly comprised of randomized tests and tests of functions that are computationally demanding.
	\item Other test suites:
		They comprise tests that require third-party code.
\end{itemize}

All test suites have to execute without errors before the release of a new CORA version.